---
title: "Final Presentation"
author: "Chris Kardish and Marie Agosta"
date: "December 2, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Research Question 

*In the US, do traditional indicators of voter turnout hold the same amount of predictive power across generations?* 

Traditional indicators of voter turnout: 
- income 
- martital status 
- age
- occupation
- education 

For example, education is a traditional indicator used to assess the liklihood that you'll vote but how storng is it for the millenials compared to baby boomers? Are there other variables that would hold more predictive power for Millenials, such as race or gender? 

## It Matters

Approximately 69.2 million Millenials are of voting age and are eligible to vote, making them the largest share of eligible voters. Yet...

- 50% voted in the 2008 presidential election 
- 46% voted in the 2012 election 

And... 

- Millenials are demographically much more diverse than previous generations  
- Millenials came of age in a very secular and technology driven world 

## Methodology 

We opted for a logit model. We wanted to assess the probabilty of a baby boomer or millenial, for example, voting in 2012, dependent upon income, education, race, and gender. 

Our independent variables are: 
- education
- gender
- income
- race
- Voted in 2008 

## Choice of Data 

- American National Election Studies 
- Face to face and internet survey, N = 4,505
- Response Rates: 
    - Face-to-face: 38 percent
    - Online: 2 percent
- Over 1,900 variables
- Conducted in English and Spanish 
- Weighted survey 

## Some findings 

black, women and men
white, women and men 

```{r cars, echo = TRUE}
summary(cars)
```

```{r pressure}
plot(pressure)
```

## Discussion 

- November 8th, 2016 
- external valididty with only 2012
- Self surveys 


